Poincar\'e--Friedrichs constants over triangulated domains

### 2024-05-01 main.tex
Update on Overleaf.

% 2. Develop manifold-like complexes and characterize them 
\subsection{Triangulations of manifolds}

We call an $n$-dimensional simplicial complex $\calT$ \emph{non-branching} if every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. We call those $F \in \calT$ of dimension $n-1$ contained within only one parent a \emph{boundary face}.
We write $\partial\calT$ for the simplicial subcomplex of $\calT$ of dimension $n-1$ 
whose full-dimensional members are exactly the boundary faces of $\calT$.

@@

\section{Constructive estimate of $p$-Poincar\'e constants}

% See the collection at Lemma 3.24
% https://hal.science/hal-03226049/file/volI_hal.pdf

We now collect examples for Poincar\'e--Friedrich inequalities for important special cases; see also~\cite{ern2021finite} for a short overview. Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Moreover, when $1 < p < \infty$, we know~\cite{chua2006estimates} that
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align}
In addition to that,
according to~\cite[Theorem~1]{esposito2013poincare}, when $2 \leq p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{ENT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{\rm{ENT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
The constant $C_{\rm{ENT},p}$ is the best possible. 
Note that the last inequalities imply, again when $2 \leq p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{1-\frac 2 p}C_{\rm{ENT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case.

\begin{remark}
    Let us compare the different estimates for the Poincar\'e inequality in the case $2 \leq p$. 
    We observe 
    \begin{align*}
        2^{1-\frac 2 p}
        C_{\rm{ENT},p}
        =
        2 
        \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 4^{\frac 1 p} }
        =
        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  \sqrt[p]{p-1}  }
        \leq 
        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  }
        \leq 
        \frac{1}{ 4^{\frac 1 p} }
        .
    \end{align*}
    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden}.
    In the limit as $p$ goes to infinity, \eqref{math:esposito:poincare} implies the Poincar\'e inequality 
    \begin{align*}
        \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
        \leq 
        \diam(\Omega)
        \| \nabla u \|_{L^{\infty}(\Omega)}
        ,
        \quad
        u \in W^{1,\infty}(\Omega)
        %
    \end{align*}
    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. 
    Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
%     Taking the \emph{informal} limit also suggest the inequality 
%     \begin{align*}
%         \min\limits_{ c \in \bbR }
%         \| u - c \|_{L^{\infty}(\Omega)}
%         \leq 
%         \frac{d}{2}
%         \| \nabla u \|_{L^{\infty}(\Omega)}
%         ,
%         \quad
%         u \in W^{1,\infty}(\Omega)
%         ,
%     \end{align*}
%     however, we generally cannot exchange the minimum and the limit, so that is strictly informal. 
\end{remark}

% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
% d/2 in the case $p = 1$ over convex domains

\section{Constructive estimate of $p$-Poincar\'e--Friedrichs constants}
% Repeat for H(curl), H(div), and differential forms

>>>>

\section{Constructive estimate of Poincar\'e constants}

In this section we address the stepwise computable estimate of Poincar\'e constants of triangulated domains. As a preparatory step, we survey variations of the Poincar\'e inequality over convex domains. These results, the exposition of which we believe to be of value on its own, will serve as a building block in constructing inequalities over triangulated domains.

\subsection{Poincar\'e inequalities over convex domains}
% See the collection at Lemma 3.24
% https://hal.science/hal-03226049/file/volI_hal.pdf

We now collect examples for Poincar\'e--Friedrich inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Moreover, when $1 < p < \infty$, we know~\cite{chua2006estimates} that
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align}
In addition to that,
according to~\cite{ferone2012remark,esposito2013poincare}, when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{ENT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{\rm{ENT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
The constant $C_{\rm{ENT},p}$ is the best possible. 
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{1-\frac 2 p}C_{\rm{ENT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case.

\begin{remark}
    Let us compare the different estimates for the Poincar\'e inequality in the case $2 \leq p$. 
    We observe 
    \begin{align*}
        2^{1-\frac 2 p}
        C_{\rm{ENT},p}
        =
        2 
        \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 4^{\frac 1 p} }
        =
        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  \sqrt[p]{p-1}  }
        \leq 
        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  }
        \leq 
        \frac{1}{ 4^{\frac 1 p} }
        .
    \end{align*}
    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden} for $p \geq 2$.
    In the limit as $p$ goes to $1$, \eqref{math:esposito:poincare} recovers \eqref{math:acostaduran}. 
    In the limit as $p$ goes to infinity, \eqref{math:esposito:poincare} implies the Poincar\'e inequality 
    \begin{align*}
        \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
        \leq 
        \diam(\Omega)
        \| \nabla u \|_{L^{\infty}(\Omega)}
        ,
        \quad
        u \in W^{1,\infty}(\Omega)
        %
    \end{align*}
    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. 
    Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
%     Taking the \emph{informal} limit also suggest the inequality 
%     \begin{align*}
%         \min\limits_{ c \in \bbR }
%         \| u - c \|_{L^{\infty}(\Omega)}
%         \leq 
%         \frac{d}{2}
%         \| \nabla u \|_{L^{\infty}(\Omega)}
%         ,
%         \quad
%         u \in W^{1,\infty}(\Omega)
%         ,
%     \end{align*}
%     however, we generally cannot exchange the minimum and the limit, so that is strictly informal. 
\end{remark}

\begin{align}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    % 2^{ - \frac{p-1}{p}}
    %2^{ - 1 + \frac{1}{p}}
    \frac{1}{ 2^{ 1 - \frac{1}{p} } }
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
% d/2 in the case $p = 1$ over convex domains

\begin{proof}
    Given $z \in \Omega$, we define 
    \[
        u_z(x) := \int_0^1 \bff( z + t(x-z) ) \cdot (x-z)
    \]
\end{proof}

\subsection{Poincar\'e inequalities over triangulated domains}

\section{Shellable triangulated domains}

% 2. Develop manifold-like complexes and characterize them 
We call an $n$-dimensional simplicial complex $\calT$ \emph{non-branching} if every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. We call those $F \in \calT$ of dimension $n-1$ contained within only one parent a \emph{boundary face}.
We write $\partial\calT$ for the simplicial subcomplex of $\calT$ of dimension $n-1$ 
whose full-dimensional members are exactly the boundary faces of $\calT$.

@@

\section{Constructive estimate of Poincar\'e--Friedrichs constants}
% Repeat for H(curl), H(div), and differential forms
